%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage{enumitem}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{xcolor}
\usepackage{mdframed}
\usepackage{tcolorbox}

\input{glyphtounicode}

%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \scshape\raggedright\large
}{}{0 em}{}[\color{black}\titlerule]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands

% Add graybox functionality
\newmdenv[
  backgroundcolor=gray!20,
  innertopmargin=-7pt,
  innerbottommargin=10pt,
  innerrightmargin=false,
  innerleftmargin=2pt,
  leftmargin=-10pt,
  outerlinecolor=gray!20,
  topline=false,
  leftline=false,
  bottomline=false,
  rightline=false,
  leftmargin=-1em, 
  linewidth=4pt,    
  skipbelow=0
]{graybox}
\AtBeginEnvironment{graybox}{\vspace{-4pt}}
\AtEndEnvironment{graybox}{\vspace{-4pt}}

\newcommand{\customsize}[2]{\fontsize{#1}{#2}\selectfont}

\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

\newcommand{\resumeItem}[1]{
  \item\small{
    {#1}
  }
}

\newcommand{\resumeSubheading}[4]{
  \item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}
}

\newcommand{\resumeProjectHeading}[2]{
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=0pt]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\newcommand{\resumeProjectListStart}{\begin{itemize}[leftmargin=0pt, label={}]} 
\newcommand{\resumeProjectListEnd}{\end{itemize}}
\newcommand{\resumeProjectItemListStart}{%
  \begin{itemize}[leftmargin=*, topsep=0, itemsep=0, parsep=0pt, partopsep=0pt]}
\newcommand{\resumeProjectItemListEnd}{\end{itemize}}
%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    \textbf{\Huge \scshape Alexander Joos} \\ \vspace{1pt}
    \small +1-978-799-9242 $|$ \href{mailto:aaj46@cornell.edu}{\underline{aaj46@cornell.edu}} $|$ 
    \href{https://linkedin.com/in/alexanderjoos1}{\underline{linkedin.com/in/alexanderjoos1}} 
    % $|$
    % \href{https://github.com/alexanderjoos}{\underline{github.com/alexanderjoos}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart

    \begin{graybox}
    \resumeSubheading
      {Cornell University}{Ithaca, NY}
      {B.A. Information Science (Data Science); GPA - 3.7}{Aug. 2022 -- Dec. 2025}
    \resumeSubSubheading
      {MEng Computer Science}{ Jan. 2026 -- Dec. 2026}
    \resumeSubheading
      {National University of Singapore}{Singapore}
      {Yale NUS College Exchange Program}{Jan. 2025 - May 2025}
    \end{graybox}

    
    \begin{itemize}[leftmargin=-10pt, label={}]
    \item{
    \textbf{(select) Coursework:}
    {\small{{Machine Learning (Graduate), Software Engineering (Graduate), Data Structures \& Algorithms, Data Science, Data Mining, Backend Development, Object-Oriented Programming, Algorithm Design (Graduate), Deep Learning (Graduate), Statistics, Linear Algebra, Text Mining, LLM's, Functional Programming, Networking (Graduate), Computer Organization, Discrete Math, Web Dev, Calculus II, Tech Communication}
    }}}
    \end{itemize}
    %Additional classes to addEquitable Computing, General Chemistry, Ecological Biology, Environmental Science
    \resumeSubHeadingListEnd 
%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \begin{graybox}
    \resumeSubheading
      {Graduate Data Engineering Intern (Incoming)}{June 2026 -- Aug. 2026}
      {Fidelity Investments, TBD}{TBD}
    \end{graybox}
    
    \begin{graybox}
    \resumeSubheading
      {Data Engineering Intern}{June 2025 -- Aug. 2025}
      {Fidelity Investments, Cloud and Platform Engineering}{Merrimack, NH}
    \end{graybox}
      \resumeItemListStart
        \resumeItem{Developed, led cross-timezone KT trainings, and launched flask/AJAX based internal Ubuntu VM based webapp.}
        \resumeItem{Supported data model comparison across DBs (Oracle, Postgres, CRDB, Snowflake) within the brokerage platform.}
        \resumeItem{Implemented architecture, data storage and retrieval via Python/SQL \& front end via JavaScript/HTML/CSS/Flask.}
        \resumeItem{Deployed Apache Webserver, TSD, SSL certification, firewall whitelisting, and OP/DEV/PROD launch.}
      \resumeItemListEnd 
% -----------Multiple Positions Heading-----------
%    \resumeSubSubheading
%     {Software Engineer I}{Oct 2014 - Sep 2016}
%     \resumeItemListStart
%        \resumeItem{Apache Beam}
%          {Apache Beam is a unified model for defining both batch and streaming data-parallel processing pipelines}
%     \resumeItemListEnd
%    \resumeSubHeadingListEnd
% -------------------------------------------
    \begin{graybox}
    \resumeSubheading
      {Data Analytics Intern}{May 2024 -- Aug. 2024}
      {American Family Insurance: Homesite}{Boston, MA}
    \end{graybox}
      \resumeItemListStart
        \resumeItem{Conducted data engineering in Google Cloud Platform on Fortune 50 retailer to aid Google Cloud data migration.}
        \resumeItem{Built data architecture \& dashboard suite for Partner Management \& Executive Team in Looker Studio.}
        \resumeItem{Programmed app scripts in Excel and Sheets in JavaScript and VBA to tailor functionality to business needs.}
       \resumeItemListEnd
     \begin{graybox}
     \resumeSubheading
       {Partner Distribution Intern}{June 2023 -- Aug. 2023}
        {American Family Insurance: Homesite}{Boston, MA}
     \end{graybox}
       \resumeItemListStart
         \resumeItem{Conducted Excel analysis on distribution partner \& top US auto carrier to infer competition feature importance.}
         \resumeItem{Formulated semi-annual internal \& external reports leveraging Power Pivot/Power Query built dashboard.}
       \resumeItemListEnd
    \begin{graybox}
    \resumeSubheading
      {Guide}{Oct. 2022 -- Present}
      {Cornell Outdoor Odyssey}{Ithaca, NY}
    \end{graybox}
      \resumeItemListStart
        \resumeItem{Lead and mentor \textasciitilde10 incoming freshmen on 5–9-night backpacking trips on New York State trails.}
        \resumeItem{Teach outdoor skills, build community, and foster an inclusive environment for students entering their first semester.}
      \resumeItemListEnd
    \begin{graybox}
    \resumeSubheading
      {Co-founder / Owner}{2018 -- 2022}
      {Results Lawn Care: Landscaping Business}{Westford, MA}
    \end{graybox}
      \resumeItemListStart
        \resumeItem{Managed operations and scheduling for 40+ recurring landscape maintenance customers.}
        \resumeItem{Designed and maintained business website and coordinated customer communication.}
      \resumeItemListEnd
   \resumeSubHeadingListEnd
%-----------PROJECTS----------- graybox stuff is vibe coded prolly should fix with standard tcolorbox
%--------------------------------------------------------------------------------------------------
%--------------------------------------------------------------------------------------------------
\section{Projects}
\resumeProjectListStart
    \item
    \begin{tcolorbox}[colback=gray!20, colframe=white, boxrule=0 pt, arc=0 pt, left=-1 pt, right=-4 pt, top=-1 pt, bottom=8 pt]
    \resumeProjectHeading {\textbf{Open Source Systems \& Anomaly Detection:} \customsize{9}{11}{\emph{Apache Airflow Anomaly Detection }}}{Ongoing}
    \end{tcolorbox}%
    \resumeProjectItemListStart
    \resumeItem{Serving as Project Lead for 4-person Agile SWE team building an Airflow feature in a fork of Apache Airflow to detect anomalous task runtimes from historical DAG execution data in Python.}
    \resumeProjectItemListEnd
%--------------------------------------------------------------------------------------------------
    \begin{tcolorbox}[colback=gray!20, colframe=white, boxrule=0 pt, arc=0 pt, left=-1 pt, right=-4 pt, top=-1 pt, bottom=8 pt]
    \resumeProjectHeading
    {\textbf{Full-Stack Mobile Development:} \customsize{9}{11}{\emph{Coursly (Course Review App)}}}{Nov. 2025}
    \end{tcolorbox}%
    \resumeProjectItemListStart
    \resumeItem{Built backend for a full-stack Cornell course review app, supporting course browsing, search, saves, and user profiles.}
    \resumeItem{Developed Flask REST APIs, scraping pipeline, data model (SQLite), containers (Docker Compose), \& deployed in GCP.}
    \resumeProjectItemListEnd
%--------------------------------------------------------------------------------------------------
    \begin{tcolorbox}[colback=gray!20, colframe=white, boxrule=0 pt, arc=0 pt, left=-1 pt, right=-4 pt, top=-1 pt, bottom=8 pt]
    \resumeProjectHeading
    {\textbf{Functional Programming \& Game Development:} \customsize{9}{11}{\emph{OCamlPacman}}}{Oct. 2025}
    \end{tcolorbox}%
    \resumeProjectItemListStart
    \resumeItem{Co-Built Pac-Man GUI game from scratch in OCaml, implementing modular mazes \& ghost AI. \href{https://www.youtube.com/watch?v=nqBE4g7SEJE}{\underline{YouTube Demo}}}
    \resumeProjectItemListEnd
%--------------------------------------------------------------------------------------------------
    \begin{tcolorbox}[colback=gray!20, colframe=white, boxrule=0 pt, arc=0 pt, left=-1 pt, right=-4 pt, top=-1 pt, bottom=8 pt]
    \resumeProjectHeading
    {\textbf{NLP \& Unsupervised ML:} \customsize{9}{11}{\emph{Clustering Analysis on Workplace Gender \& Power}}}{Dec. 2024}
    \end{tcolorbox}%
    \resumeProjectItemListStart
    \resumeItem{LLM-cleaned email bodies into a high-dimensional TF-IDF matrix, capturing sentiment across 15,000+ messages.}
    \resumeItem{Utilize DBSCAN, K-means, \& Cross Tabulation approaches, analyzing Gender-Power-Positional clusters.}
    \resumeProjectItemListEnd
%--------------------------------------------------------------------------------------------------
    \begin{tcolorbox}[colback=gray!20, colframe=white, boxrule=0 pt, arc=0 pt, left=-1 pt, right=-4 pt, top=-1 pt, bottom=8 pt]
    \resumeProjectHeading
    {\textbf{LLM Fine-Tuning \& Classification:} \customsize{9}{11}{\emph{Old Bailey Verdict Prediction Model}}}{Nov. 2024}
    \end{tcolorbox}%
    \resumeProjectItemListStart
    \resumeItem{Fine-tuned Huggingface LLM on 300+ years of $>$100,000 Old Bailey case briefs (8 legal categories).}
    \resumeItem{Performed “GUILTY” vs. “NOT GUILTY” classification, achieving 71\% weighted avg f1, outperforming baseline.}
    \resumeProjectItemListEnd
%--------------------------------------------------------------------------------------------------
    \begin{tcolorbox}[colback=gray!20, colframe=white, boxrule=0 pt, arc=0 pt, left=-1 pt, right=-4 pt, top=-1 pt, bottom=8 pt]
    \resumeProjectHeading
    {\textbf{Data Mining \& Risk Analysis in R:} \customsize{9}{11}{\emph{Measuring Dangerous Roads in Chicago}}}{May 2023}
    \end{tcolorbox}%
    \resumeProjectItemListStart
    \resumeItem{As a group, analyzed {\raise.17ex\hbox{$\scriptstyle\mathtt{\sim}$}} 800,000 datapoints relating to Chicago 2023 car crashes relating features and fatalities.}
    \resumeItem{Utilized PCA, linear \& logistic regression, hierarchal clustering, k-means clustering, cross-validation, \& regularization.}
    \resumeProjectItemListEnd
%--------------------------------------------------------------------------------------------------
    \begin{tcolorbox}[colback=gray!20, colframe=white, boxrule=0 pt, arc=0 pt, left=-1 pt, right=-4 pt, top=-1 pt, bottom=8 pt]
    \resumeProjectHeading
    {\textbf{Feature Engineering \& Web Scraping:} \customsize{9}{11}{\emph{Socioeconomic Factors Influencing Alien Sightings}}}{Dec. 2023}
    \end{tcolorbox}%
    \resumeProjectItemListStart
    \resumeItem{Merged global datasets on education, religion, drug use, and wealth to analyze sociocultural trends in alien sightings.}
    \resumeItem{Used BeautifulSoup for large-scale scraping and scikit-learn for feature analysis and regression modeling.}
    \resumeProjectItemListEnd
    \resumeProjectListEnd
%-----------PROGRAMMING SKILLS-----------
\section{Skills}
 \begin{itemize}[leftmargin=0pt, label={}]
    \small{\item{
     \textbf{Back-end Development Tools}{: Python (pytest), Java (JUnit), OCaml (OUnit), C/C++, Bash, REST API, OOP, DSA} \\
     \textbf{Analytics \& Front-end Tools}{: SQL, R, HTML, CSS, JavaScript, Flask, SQLite, Apache Airflow} \\
     \textbf{Developer Tools}{: GitHub, Git, Docker (Compose), VS Code, PuTTY, Bash, Ubuntu,  RStudio, Google Colab, Jupyter} \\
     \textbf{Enterprise Tools}{: BigQuery, Vertex AI, Looker, Power BI, DBeaver, Agile, Jira, Excel, PowerPoint, Tableau, Confluence } \\
     \textbf{Libraries}{: scikit-learn, PyTorch, transformers, pandas, NumPy, matplotlib, bs4, oracledb, SQLAlchemy, ggplot2, tidyverse} \\
     %-----------(INSIDE SKILLS) INTERESTS SECTION--------------%
     \vspace{-1 pt}\begin{tcolorbox}[colback=gray!20, colframe=white, boxrule=0 pt, arc=0 pt, left=-2 pt, right=-4 pt, top=1 pt, bottom=1 pt]
        \textbf{Interests}{: Hiking, German Language, Climbing, Anime, Board Games, Soccer, Volleyball, Service Projects, Pizza Making}
     \end{tcolorbox}\vspace{0 pt}
     %----------------------------------------------------------
}}
\end{itemize}
%-------------------------------------------
\end{document}
