\documentclass[letterpaper,11pt]{article}

\usepackage[margin=0.5in]{geometry}
\usepackage{titlesec}
\usepackage[letterpaper,margin=0.5in]{geometry}
\usepackage[hidelinks]{hyperref}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage[most]{tcolorbox}
\usepackage{tabularx}
\usepackage{microtype}

\pagestyle{empty}
\setlength{\parindent}{0pt}
\setlength{\tabcolsep}{0pt}

\titleformat{\section}{\scshape\raggedright\large}{}{0em}{}[\titlerule]
\titlespacing*{\section}{0pt}{6pt}{4pt}

\newcommand{\bulletfont}{\fontsize{9.8}{10.9}\selectfont}
\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}

\setlist[itemize]{
  leftmargin=0.6em,
  labelsep=0.25em,
  topsep=1pt,
  itemsep=3pt,  
  parsep=0pt,
  partopsep=0pt,
  before=\bulletfont
}

\tcbset{
  resumebox/.style={
    enhanced,
    colback=gray!15,
    colframe=white,
    boxrule=0pt,
    arc=0pt,
    left=4pt,
    right=4pt,
    top=2pt,
    bottom=2pt,
    boxsep=0pt,
    width=\linewidth,
    before skip=5pt,
    after skip=3pt
  }
}

\usepackage{enumitem}

\usepackage{tabularx} % if not already included

\newcommand{\projheader}[3]{%
  \begin{tcolorbox}[resumebox]
    \begin{tabularx}{\linewidth}{@{}Xr@{}}
      \small \textbf{#1:} \textit{#2} & \small #3
    \end{tabularx}
  \end{tcolorbox}
}

\begin{document}

% ===== HEADER =====
\begin{center}
    {\Huge\bfseries\scshape Alexander Joos}\\[-1pt]
    \small
    +1-978-799-9242 $|$
    \href{mailto:aaj46@cornell.edu}{\underline{aaj46@cornell.edu}} $|$
    \href{https://linkedin.com/in/alexanderjoos1}{\underline{linkedin.com/in/alexanderjoos1}}
\end{center}

% ----------- EDUCATION -----------
\section{Education}

\begin{tcolorbox}[resumebox]
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{Cornell University} & Ithaca, NY \\
\textit{B.A. Information Science (Data Science); GPA: 3.64} & \textit{Aug.\ 2022 -- Dec.\ 2025} \\
\textit{MEng Computer Science} & \textit{Jan.\ 2026 -- Dec.\ 2026} \\
\textbf{National University of Singapore} & Singapore \\
\textit{Yale NUS College Exchange Program} & \textit{Jan.\ 2025 -- May\ 2025} \\
\end{tabular*}
\end{tcolorbox}

{\small
\textbf{(select) Coursework:}
Machine Learning (Graduate), Software Engineering (Graduate), Data Structures \& Algorithms,
Data Science, Data Mining, Backend Development, Object-Oriented Programming, Algorithm Design (Graduate),
Deep Learning (Graduate), Statistics, Linear Algebra, Text Mining, LLMs, Functional Programming,
Networking (Graduate), Computer Organization, Discrete Math, Web Dev, Calculus II, Tech Communication}

% ----------- EXPERIENCE -----------
\section{Experience}

\begin{tcolorbox}[resumebox]
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{Graduate Data Engineering Intern (Incoming)} & June 2026 -- Aug.\ 2026 \\
\textit{\small Fidelity Investments, TBD} & \textit{\small TBD} \\
\end{tabular*}
\end{tcolorbox}

\begin{tcolorbox}[resumebox]
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{Data Engineering Intern} & June 2025 -- Aug.\ 2025 \\
\textit{\small Fidelity Investments, Cloud and Platform Engineering} & \textit{\small Merrimack, NH} \\
\end{tabular*}
\end{tcolorbox}
\begin{itemize}
    \item Developed, led cross-timezone KT trainings, and launched Flask/AJAX-based internal Ubuntu VM web app.
    \item Supported data model comparison across DBs (Oracle, PostgreSQL, CRDB, Snowflake) within the brokerage platform.
    \item Implemented architecture, data storage/retrieval in Python/SQL and front end in JavaScript/HTML/CSS/Flask.
    \item Deployed Apache web server, TSD, SSL certification, firewall whitelisting, and OP/DEV/PROD launch.
\end{itemize}

\begin{tcolorbox}[resumebox]
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{Data Analytics Intern} & May 2024 -- Aug.\ 2024 \\
\textit{\small American Family Insurance: Homesite} & \textit{\small Boston, MA} \\
\end{tabular*}
\end{tcolorbox}
\begin{itemize}
    \item Conducted data engineering in Google BigQuery on a Fortune 50 retailer project to support Google Cloud migration.
    \item Built data architecture and dashboard suite for Partner Management and Executive Team in Looker Studio.
    \item Programmed app scripts in Excel and Sheets using JavaScript and VBA to tailor functionality to business needs.
\end{itemize}

\begin{tcolorbox}[resumebox]
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{Partner Distribution Intern} & June 2023 -- Aug.\ 2023 \\
\textit{\small American Family Insurance: Homesite} & \textit{\small Boston, MA} \\
\end{tabular*}
\end{tcolorbox}
\begin{itemize}
    \item Conducted Excel analysis on a distribution partner and top U.S.\ auto carrier to infer competition feature importance.
    \item Formulated semi-annual internal and external reports leveraging a Power Pivot / Power Query dashboard.
\end{itemize}

\begin{tcolorbox}[resumebox]
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{Guide} & Oct.\ 2022 -- Present \\
\textit{\small Cornell Outdoor Odyssey} & \textit{\small Ithaca, NY} \\
\end{tabular*}
\end{tcolorbox}
\begin{itemize}
    \item Lead and mentor $\sim 10$ incoming freshmen on 5 to 9 night backpacking trips on New York State trails.
    \item Teach outdoor skills, build community, and foster an inclusive environment for students entering their first semester.
\end{itemize}

\begin{tcolorbox}[resumebox]
\begin{tabular*}{\linewidth}{@{}l@{\extracolsep{\fill}}r@{}}
\textbf{Co-founder / Owner} & 2018 -- 2022 \\
\textit{\small Results Lawn Care: Landscaping Business} & \textit{\small Westford, MA} \\
\end{tabular*}
\end{tcolorbox}
\begin{itemize}
    \item Managed operations and scheduling for 40+ recurring landscape maintenance customers.
    \item Designed and maintained business website and coordinated customer communication.
\end{itemize}

% ----------- PROJECTS -----------
\section{Projects}

\projheader{Open Source Systems \& Anomaly Detection}{Apache Airflow Anomaly Detection}{Ongoing}
\begin{itemize}
    \item Serving as Project Lead for a 4-person Agile SWE team building a feature in a fork of Apache Airflow to detect anomalous task runtimes from historical DAG execution data in Python.
\end{itemize}

\projheader{Full-Stack Mobile Development}{Coursly (Course Review App)}{Nov.\ 2025}
\begin{itemize}
    \item Built backend for a full-stack Cornell course review app, supporting course browsing, search, saves, and user profiles.
    \item Developed Flask REST APIs, scraping pipeline, data model (SQLite), containers (Docker Compose), and deployed in GCP.
\end{itemize}

\projheader{Functional Programming \& Game Development}{OCamlPacman}{Oct.\ 2025}
\begin{itemize}
    \item Co-built Pac-Man GUI game from scratch in OCaml, implementing modular mazes and ghost AI. \href{https://www.youtube.com/watch?v=nqBE4g7SEJE}{\underline{YouTube Demo}}
\end{itemize}

\projheader{NLP \& Unsupervised ML}{Clustering Analysis on Workplace Gender \& Power}{Dec.\ 2024}
\begin{itemize}
    \item LLM-cleaned email bodies into a high-dimensional TF-IDF matrix, capturing sentiment across 15{,}000+ messages.
    \item Used DBSCAN, K-means, and cross-tabulation approaches to analyze gender-power-positional clusters.
\end{itemize}

\projheader{LLM Fine-Tuning \& Classification}{Old Bailey Verdict Prediction Model}{Nov.\ 2024}
\begin{itemize}
    \item Fine-tuned a Hugging Face LLM on 300+ years of \(>100{,}000\) Old Bailey case briefs (8 legal categories).
    \item Performed ``GUILTY'' vs.\ ``NOT GUILTY'' classification, achieving 71\% weighted-average F1 and outperforming baseline.
\end{itemize}

\projheader{Data Mining \& Risk Analysis in R}{Measuring Dangerous Roads in Chicago}{May 2023}
\begin{itemize}
    \item As a group, analyzed \(\sim 800{,}000\) datapoints on 2023 Chicago car crashes, relating features and fatalities.
    \item Utilized PCA, linear and logistic regression, hierarchical clustering, K-means clustering, cross-validation, and regularization.
\end{itemize}

\projheader{Feature Engineering \& Web Scraping}{Socioeconomic Factors Influencing Alien Sightings}{Dec.\ 2023}
\begin{itemize}
    \item Merged global datasets on education, religion, drug use, and wealth to analyze sociocultural trends in alien sightings.
    \item Used BeautifulSoup for large-scale scraping and scikit-learn for feature analysis and regression modeling.
\end{itemize}

% ----------- SKILLS -----------
\section{Skills}

{\small
\textbf{Back-end Development Tools:} Python (pytest), Java (JUnit), OCaml (OUnit), C/C++, Bash, REST API, OOP, DSA\\
\textbf{Analytics \& Front-end Tools:} SQL, R, HTML, CSS, JavaScript, Flask, SQLite, Apache Airflow\\
\textbf{Developer Tools:} GitHub, Git, Docker (Compose), VS Code, PuTTY, Bash, Ubuntu, RStudio, Google Colab, Jupyter\\
\textbf{Enterprise Tools:} BigQuery, Vertex AI, Looker, Power BI, DBeaver, Agile, Jira, Excel, PowerPoint, Tableau, Confluence\\
\textbf{Libraries:} scikit-learn, PyTorch, transformers, pandas, NumPy, matplotlib, bs4, oracledb, SQLAlchemy, ggplot2, tidyverse
}

\begin{tcolorbox}[resumebox, width=\linewidth, left=0pt, right=0pt, boxsep=0pt]
\small \textbf{Interests:} Hiking, German Language, Climbing, Anime, Board Games, Soccer, Volleyball, Service Projects, Pizza Making
\end{tcolorbox}

\end{document}
